Make any stupid plot you want

### 2021-04-20 draft/sections/intro.tex
housekeeping

One of the reasons we developed a new formalism rather than adopting the architecture of an existing library is that most information visualization software design patterns, as categorized by Heer and Agrawala\cite{HeerSoftware2006}, are tuned to very specific data structures. These libraries can often assume the expected data structure because they are domain specific, and that is the common data structure in that domain.  For users who generally work in one domain, such as the data, networks, or graphs shown in \autoref{fig:intro:data}, this well defined data space (and corresponding visual space\cite{chiTaxonomyVisualizationTechniques2000}) often yields a very coherant user experience\cite{heerDeclarative2010}. But, for developers who want to build new visualizations on top of these libraries, they must work around the existing assumptions, sometimes in ways that break the model the libraries are developed around.

>>>>

One of the reasons we developed a new formalism rather than adopting the architecture of an existing library is that most information visualization software design patterns, as categorized by Heer and Agrawala\cite{HeerSoftware2006}, are tuned to very specific data structures. These libraries can often assume the expected data structure because they are domain specific, and that is the common data structure in that domain.  For users who generally work in one domain, such as the data, networks, or graphs shown in \autoref{fig:intro:data}, this well defined data space (and corresponding visual space\cite{chiTaxonomyVisualizationTechniques2000}) often yields a very coherent user experience\cite{heerDeclarative2010}. But, for developers who want to build new visualizations on top of these libraries, they must work around the existing assumptions, sometimes in ways that break the model the libraries are developed around.

### 2021-04-20 draft/sections/math.tex
housekeeping

\subsubsection{Composition of Artists: +}
\begin{figure}[H]
\begin{subfigure}{.5\textwidth}
    \includegraphics[width=1\textwidth]{figures/math/exploding_artist.png}
    \caption{}
    \label{fig:math:seperate}    
\end{subfigure}
\begin{subfigure}{.5\textwidth}
    \includegraphics[width=1\textwidth]{figures/math/combined_artist.png}
    \caption{}
    \label{fig:math:combined}
\end{subfigure}
\caption{Each of the visual elements in \autoref{fig:math:seprate} is generated via a unique artist \vartist. In \autoref{fig:math:seperate}, they are added to the image independent of the other elements, creating an incoherant visualization. In \autoref{fig:math:combined}, these artists are composited before being added to the image. Disjoint union of \dtotal\ aligns the two timeseries with the x and y axis so all these elements use a shared coordinate system. A more complex composition dictates that the legend is connected to the \dtotal\ such that it must use the same color as the data it is identifying.}
\label{fig:artist_plus}
\end{figure}
Visualizations with a single artist do not provide much information, so we define addition operators for generating more complex visualizations. Given the family of artists $(\dtotal_i: i\in I)$ on the same image, the + operator 
\begin{equation}
+ \coloneqq \underset{i\in I}{\sqcup} \dtotal_{i}
\end{equation}
defines a simple composition of artists. For example, the components in \autoref{fig:math:seperate} are each generated by different artists, and a visualization of solely the x axis is rarely all that useful. In \autoref{fig:math:seperate}, these artists are all added to the image independently of the other and therefore there are no constraints on how they are generated in conjunction with each other. In \autoref{fig:math:combined}, the data is joined via disjoint union; doing so aligns the components in \dfiber\ such the \vchannel\ to the same component in \vfiber\ targets the same coordinate system. When artists share a base space $\dbase_2 \hookrightarrow \dbase_1$, a composition operator can be defined such that the artists are acting on different components of the same section. This type of composition is important for visualizations where elements update together in a consistent way, such as multiple views \cite{alboRadarComparativeEvaluation2016a, hullmanKeeping2018} and brush-linked views\cite{beckerBrushingScatterplots1987,bujaInteractiveData1991}.

>>>>

\subsubsection{Composition of Artists: +}
\begin{figure}[H]
\begin{subfigure}{.5\textwidth}
    \includegraphics[width=1\textwidth]{figures/math/exploding_artist.png}
    \caption{}
    \label{fig:math:seperate}    
\end{subfigure}
\begin{subfigure}{.5\textwidth}
    \includegraphics[width=1\textwidth]{figures/math/combined_artist.png}
    \caption{}
    \label{fig:math:combined}
\end{subfigure}
\caption{Each of the visual elements in \autoref{fig:math:seprate} is generated via a unique artist \vartist. In \autoref{fig:math:seperate}, they are added to the image independent of the other elements, creating an incoherant visualization. In \autoref{fig:math:combined}, these artists are composited before being added to the image. Disjoint union of \dtotal\ aligns the two timeseries with the x and y axis so all these elements use a shared coordinate system. A more complex composition dictates that the legend is connected to the \dtotal\ such that it must use the same color as the data it is identifying.}
\label{fig:artist_plus}
\end{figure}
We describe the constraints for compositing artists by defining addition operators. Given the family of artists $(\dtotal_i: i\in I)$ that are rendered to the same image, the + operator 
\begin{equation}
+ \coloneqq \underset{i\in I}{\sqcup} \dtotal_{i}
\end{equation}
defines a simple composition of artists. For example, the components in \autoref{fig:math:seperate} are each generated by different artists, and a visualization of solely the x axis is rarely all that useful. In \autoref{fig:math:seperate}, these artists are all added to the image independently of the other and therefore there are no constraints on how they are generated in conjunction with each other. In \autoref{fig:math:combined}, the data is joined via disjoint union; doing so aligns the components in \dfiber\ such the \vchannel\ to the same component in \vfiber\ targets the same coordinate system. When artists share a base space $\dbase_2 \hookrightarrow \dbase_1$, a composition operator can be defined such that the artists are acting on different components of the same section. This type of composition is important for visualizations where elements update together in a consistent way, such as multiple views \cite{alboRadarComparativeEvaluation2016a, hullmanKeeping2018} and brush-linked views\cite{beckerBrushingScatterplots1987,bujaInteractiveData1991}.
